---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 110)
```

# ebayr - R wrapper to the ebay Finding API

This package allows you to search ebay for **live** items using keywords, a category or both. It is a wrapper for the ebay Finding API, specifically the "findItemsAdvanced" call. You can use it after you sign up at https://go.developer.ebay.com/ and get a valid token (a.k.a AppID).

Install:

```{r Install, eval = FALSE}
devtools::install_github("gsimchoni/ebayr")
```

Load:

```{r Load}
library(ebayr)
```

Set ebay token:

```{r Set-Token, eval = FALSE}
setEbayToken("YOUR_EBAY_TOKEN")
```

Search by keywords:

```{r Search-Keywords, eval = FALSE}
search_ebay("elvis costume")
```

```{r Search-Keywords-Cache, echo = FALSE, warning = FALSE}
library(tibble)
res <- readRDS("~/readmeResults.RData")
res$keywords
```

Search by category (a.k.a Browse):

```{r Search-Category, eval = FALSE}
search_ebay(categoryName = "Video Game Consoles")
```

```{r Search-Category-Cache, echo = FALSE}
res$category
```

Search by both keywords and category:

```{r Search-Both, eval = FALSE}
search_ebay("Yahtzee", categoryName = c("Nonfiction", "Board & Traditional Games"))
```

```{r Search-Both-Cache, echo = FALSE}
res$both
```

Search the UK site for new large size Fruit of the Loom women's T-shirts from top rated sellers at a max price of 10 pounds:

```{r Search-UK, eval = FALSE}
res <- search_ebay("women's t-shirts",
                   site = "UK",
                   condition = "New",
                   listingType = "FixedPrice",
                   topRatedSellerOnly = TRUE,
                   priceRange = c(0, 10),
                   aspectFilter = list(
                     Brand = "Fruit of the Loom",
                     Size = "L"
                     )
                   )

res[, c("title", "price", "currency")]
```

```{r Search-UK-Cache, echo = FALSE}
res$uk[, c("title", "price", "currency")]
```

Search the German site for black women's handbags, ask for the 200 most expensive results:

```{r Search-DE, eval = FALSE}
res <- search_ebay("Damentaschen",
                   site = "DE",
                   sortOrder = "PricePlusShippingHighest",
                   nResults = 200,
                   aspectFilter = list(
                     Farbe = "Schwarz"
                     )
                   )

res[, c("title", "price", "currency")]
```

```{r Search-DE-Cache, echo = FALSE}
res$de[, c("title", "price", "currency")]
```

The possibilities are endless, though ebay APIs have even more.

You should probably read ebay's [API Reference](https://developer.ebay.com/Devzone/finding/Concepts/FindingAPIGuide.html) and [API license](https://go.developer.ebay.com/api-license-agreement) and make sure you adhere to the rules.

Also note that the rate limit of the API wrapped here is 5,000 requests a day, each request can bring up to 100 results (ebay items).

For more possibilities see the `search_ebay` function documentation, and read [this](http://giorasimchoni.com/2017/12/19/2017-12-19-e-is-for-elephant-the-ebayr-package/) blog post.
